---
title: "Classification of Regions with gabor filter"
author: "Eduarda Chagas"
date: "March 11, 2020"
output:
  pdf_document: default
  html_notebook: default
---

###Importing the packages

```{r}
# Load some packages: 
if(!require(caret)) install.packages("caret")
if(!require(MLmetrics)) install.packages("MLmetrics")

setwd("/home/eduarda/Desktop/Repositories/SAR/SAR-WATG-master/Code/Classification")
```

###Importing the dataset

For this analysis, three SAR images with different regions were used, they are:

* Sierra del Lacandon National Park, Guatemala (purchased April 10, 2015), available at [https://uavsar.jpl.nasa.gov/cgi-bin/product.pl?jobName=Lacand_30202_15043_
006_150410_L090_CX_01 # data] (https://uavsar.jpl.nasa.gov/cgi-bin/product.pl?jobName=Lacand_30202_15043_
006_150410_L090_CX_01 # data);

* Oceanic regions of Cape Canaveral (acquired on September 22, 2016);

* Urban area of the city of Munich, Germany (acquired on June 5, 2015).

A total of 160 samples were considered during the investigation, with 40 forest regions in Guatemala, 80 ocean regions in Cape Canaveral and 40 urban regions in the city of Munich.

```{r}
n.total = 160
regions = c(rep("Forest",40), rep("Sea",80), rep("Urban", 40))
gabor.energy = read.csv(file="../../Data/gabor.csv", header=TRUE, sep=",")
gabor = data.frame(gabor.energy, regions)

split = 0.85
trainIndex = createDataPartition(gabor$regions, p = split, list = FALSE)

x = data.frame(gabor[trainIndex,1:80])
y = factor(gabor$regions[trainIndex])

x_validation = data.frame(gabor[-trainIndex,1:80])
y_validation = factor(gabor$regions[-trainIndex])

gabor = data.frame(gabor[trainIndex,1:80], "regions" = gabor$regions[trainIndex])
```

##KNN Classifier

###Creating KNN model and predicting
```{r}
set.seed(123)
ctrl = trainControl(method="repeatedcv", number = 10, repeats = 10)
knnFit = train(regions ~., data = gabor, method = "knn", 
               trControl = ctrl, 
               preProcess = c("center","scale"), 
               tuneLength = 20)

pred = predict(knnFit, newdata = x_validation)

xtab = table(pred, y_validation)
confusionMatrix(xtab)
```


```{r}
knnFit
```

```{r}
cat("Accuracy: ", Accuracy(pred, y_validation), " Recall: ", Recall(pred, y_validation), " Precision: ", Precision(pred, y_validation), " F1-Score: ", F1_Score(pred, y_validation), "\n")
```

##SVM Classifier

###Creating SVM model and predicting

```{r}
svmFit <- train(regions ~., data = gabor, method = "svmRadial",
                 trControl=ctrl,
                 preProcess = c("center", "scale"),
                 tuneLength = 20)
pred = predict(svmFit, newdata = x_validation)

xtab = table(pred, y_validation)
confusionMatrix(xtab)
```

```{r}
cat("Accuracy: ", Accuracy(pred, y_validation), " Recall: ", Recall(pred, y_validation), " Precision: ", Precision(pred, y_validation), " F1-Score: ", F1_Score(pred, y_validation), "\n")
```

##Random Forest Classifier

###Creating Random Forest model and predicting
```{r}
rfFit <- train(regions ~., data = gabor, method = "rf", 
               trControl = ctrl, 
               preProcess = c("center","scale"), 
               tuneLength = 20)
pred = predict(rfFit, newdata = x_validation)
```

```{r}
cat("Accuracy: ", Accuracy(pred, y_validation), " Recall: ", Recall(pred, y_validation), " Precision: ", Precision(pred, y_validation), " F1-Score: ", F1_Score(pred, y_validation), "\n")
```
